jCO2 analysis

### 2016-10-09 R/jCO2_analysis.Rmd
finish comparison of jeC/jCO2 changes

# Code for new model
The rejection flux of carbon from host biomass SU, $jCw$, is used as input to photosynthesis SU. A multiplier is included indicating the number of moles of CO~2~ the host can deliver to the photosynthesis SU using one mole of fixed carbon. Mechanistically, the host will use this carbon to generate ATP to energize a variety of CO~2~-concentrating mechanisms (CCM's) that enhance CO~2~ availability to photosynthesis.
```{r new_model, include=T}
run_coral_wC <- function(time, env, pars, NPQ="inhibited", jDOC=0) {
  require(dplyr)
  # Define parallel complementary synthesizing unit function
  synth <- function(x, y, m) 1/((1/m)+(1/x)+(1/y)-(1/(x+y)))
  #synth <- function(x, y, m) (m^-2 + x^-2 + y^-2)^(-1/2)
  # Set initial values
  # ==================
  # Host
  H <- data_frame(
    time=time,
    H=pars$initH,
    jX=(pars$jXm * env$X[1] / (env$X[1] + pars$KX)),
    jCO2a=pars$jCO2a,
    jCO2p=pars$jCO2p,
    jCO2=jCO2a+jCO2p,
    jN=(pars$jNm * env$N[1] / (env$N[1] + pars$KN)),
    rhoN=jN/2,
    jCw=1,
    jHG=0.25,
    jHT=pars$jHT0,
    rNH=jHT * pars$nNH * pars$sigmaNH,
    rCH=jHT * pars$sigmaCH,
    dH.Hdt=0
  )
  H[2:nrow(H), 2:ncol(H)] <- NA

  # Symbiont
  S <- data_frame(
    time=time,
    S=.2,
    jL=env$L[1] * pars$astar,
    jCP=max(0, synth(jL * pars$nLC, (H$jCw[1] + H$jCO2p[1] + H$jCO2a[1])*H$H/S, pars$jCPm), na.rm=T),
    jeL=max(jL - jCP/pars$nLC, 0),
    jNPQ=pars$kNPQ/pars$nLC,
    jCO2w=(H$jCw + H$jCO2)*H$H/S - jCP,
    jSG=pars$jSGm/10,
    rhoC=jCP/2, 
    jNw=0,
    jST=pars$jST0,
    rNS=jST * pars$nNS * pars$sigmaNS,
    rCS=jST * pars$sigmaCS,
    cROS=1,
    dS.Sdt=1)
  S[2:nrow(S), 2:ncol(S)] <- NA

@@

    # Photosynthesis SU
    # =================
    # Light input flux
    S$jL[t] <- (1.256307 + 1.385969 * exp(-6.479055 * (S$S[t-1]/H$H[t-1]))) * env$L[t] * pars$astar
    # CO2 input flux
    H$jCO2p[t] <- pars$jCO2p # passive CO2 flux from the environment
    H$jCO2a[t] <- pars$jCO2a  # active delivery of CO2 from the environment (mediated by the host)
    H$jCO2[t] <- H$jCO2p[t] + H$jCO2a[t]  # Total CO2 input from the environment
    S$rCS[t] <- pars$jST0 * pars$sigmaCS  # metabolic CO2 recycled from symbiont biomass turnover
    H$rCH[t] <- H$jHT[t-1] * pars$sigmaCH  # metabolic CO2 recycled from host biomass turnover
    H$jCw[t-1] <- H$jCw[t-1]  # carbon rejected from host biomass SU, given back as CO2 to photosynthesis
    # Production flux (photosynthetic carbon fixation)
    S$jCP[t] <- synth(S$jL[t] * pars$nLC, (5*H$jCw[t-1] + H$jCO2[t] + H$rCH[t])*H$H[t-1]/S$S[t-1] + S$rCS[t], pars$jCPm) / S$cROS[t-1]

@@

    # Host biomass SU
    # ===============
    # Food input flux (prey=both carbon and nitrogen)
    H$jX[t] <- (pars$jXm * env$X[t] / (env$X[t] + pars$KX))  # Prey uptake from the environment
    # Nitrogen input flux
    H$jN[t] <- (pars$jNm * env$N[t] / (env$N[t] + pars$KN))  # N uptake from the environment
    H$rNH[t] <- H$jHT[t-1] * pars$nNH * pars$sigmaNH  # Recycled N from host biomass turnover
    # Carbon input flux
    S$rhoC[t] <- S$rhoC[t]  # Carbon shared by the symbiont (defined above)
    # Add dissolved organic carbon uptake
    # Production flux (host biomass formation)
    H$jHG[t] <- synth(S$rhoC[t]*S$S[t-1]/H$H[t-1] + H$jX[t] + jDOC, (H$jN[t] + pars$nNX*H$jX[t] + H$rNH[t]) / pars$nNH, pars$jHGm)
    # Rejection flux: nitrogen (surplus nitrogen shared with the symbiont)
    H$rhoN[t] <- max(H$jN[t] + pars$nNX * H$jX[t] + H$rNH[t] - pars$nNH * H$jHG[t], 0)
    # Rejection flux: carbon -- given back to symbiont as CO2 input to photosynthesis
    H$jCw[t] <- max(H$jX[t] + S$rhoC[t]*S$S[t-1]/H$H[t-1] - H$jHG[t], 0)

@@

#### possibility of DOC uptake?
```{r incr_L_DOC, cache=T, message=F, warning=F, include=F, eval=F}
# Set up simulation
env <- init_env(time=time, L=c(2,60,0), N=c(1e-7,1e-7,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, jDOC=0.005,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0)),
                 NPQ="fixed2")
plot_run_wC(run)
```

@@

### Light stress with new model
```{r Lstress_new, cache=T, message=F, warning=F}
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0)),
                 NPQ="fixed2")
plot_run_wC(run)
```

@@

# Steady state behavior of new model
```{r new_steadystates_code, message=F, warning=F, include=F}
run_steady_states <- function(time, pars, at, outfile=NULL, runtime=F, food=0, jDOC=0) {
  #
  run_coral_wC <- get("run_coral_wC")
  # Load libraries
  require(foreach)
  require(parallel)
  require(doParallel)
  require(reshape2)
  require(dplyr)

@@

  # Run simulations in parallel for each combination of "at" values
  start <- proc.time()  # Start timer...
  # Calculate steady states...
  steady_states <- foreach(i=1:nrow(at), .combine='rbind', .packages='dplyr') %dopar% {
    L <- at[i,]$L; N <- at[i,]$N
    env <- init_env(time=time, L=c(L,L,0), N=c(N,N,0), X=c(food,food,0))
    run <- run_coral_wC(time=time, env=env, pars=pars, jDOC=jDOC)
    ss <- lapply(run[c("H", "S")], function(x) x[length(time), ])
    gr <- ss$H$dH.Hdt
    sh <- ss$S$S/ss$H$H
    hl <- with(ss, log(  pmin(S$rhoC*S$S/H$H + H$jX, pars$jHGm) / pmin((H$jN + pars$nNX*H$jX + H$rNH) / pars$nNH, pars$jHGm)  ))
    sl <- with(ss, log(  pmin(S$jCP, pars$jSGm)   /   pmin((H$rhoN*H$H/S$S + S$rNS)/pars$nNS, pars$jSGm)  ))
    ee <- with(ss, max(0, S$jL - (S$jCP/run$pars$nLC + run$pars$kNPQ)))
    pl <- with(ss, log(   pmin((H$jCw + H$jCO2 + H$rCH)*H$H/S$S + S$rCS, pars$jCPm)   /   pmin(S$jL * pars$nLC, pars$jCPm)    ))
    data.frame(gr=gr, sh=sh, hl=hl, sl=sl, ee=ee, pl=pl)
  }
  stopCluster(cl)  # Stop cluster
  if (runtime==T) print(proc.time() - start)  # Print time elapsed if runtime==T

@@

## No feeding
```{r run_new_steadystates, cache=T, message=F, warning=F}
# Set time and parameters 
time <- seq(1,100,1) 
pars <- replace(defpars, c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p"), 
                          c(60,       60,    1,   5,      0.9,     0.9,       0,       0))
# Set values of L and N at which to get steady state values 
at <- expand.grid(L=seq(from=0, to=60, length.out=41),
                  N=seq(from=0, to=4e-6, length.out=41))

@@

# Stability at high nitrogen...?
## When system starts at 2 µM DIN and increases to 4 µM DIN, outcome is negative growth.
```{r incrN1, cache=T, message=F, warning=F}
# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(2e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1)),
                 NPQ="fixed2")
plot_run_wC(run)
```

## When system starts at 1 µM DIN and increases to 4 µM DIN, outcome is positive growth.
```{r incrN2, cache=T, message=F, warning=F}
# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(1e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1)),
                 NPQ="fixed2")
plot_run_wC(run)
```

>>>>

# Code for new model
The rejection flux of carbon from host biomass SU, $jCw$, is used as input to photosynthesis SU. A multiplier is included indicating the number of moles of CO~2~ the host can deliver to the photosynthesis SU using one mole of fixed carbon. Mechanistically, the host will use this carbon to generate ATP to energize a variety of CO~2~-concentrating mechanisms (CCM's) that enhance CO~2~ availability to photosynthesis.
```{r new_model, include=T}
run_coral_wC <- function(time, env, pars, NPQ="inhibited", kCO2=5) {
  require(dplyr)
  # Define parallel complementary synthesizing unit function
  synth <- function(x, y, m) 1/((1/m)+(1/x)+(1/y)-(1/(x+y)))
  #synth <- function(x, y, m) (m^-2 + x^-2 + y^-2)^(-1/2)
  # Set initial values
  # ==================
  # Host
  H <- data_frame(
    time=time,
    H=pars$initH,
    jX=(pars$jXm * env$X[1] / (env$X[1] + pars$KX)),
    jCO2a=pars$jCO2a,
    jCO2p=pars$jCO2p,
    jCO2=jCO2a+jCO2p,
    jN=(pars$jNm * env$N[1] / (env$N[1] + pars$KN)),
    rhoN=jN,
    jCw=10,
    jHG=0.25,
    jHT=pars$jHT0,
    rNH=jHT * pars$nNH * pars$sigmaNH,
    rCH=jHT * pars$sigmaCH,
    dH.Hdt=0
  )
  H[2:nrow(H), 2:ncol(H)] <- NA

  # Symbiont
  S <- data_frame(
    time=time,
    S=pars$initS,
    jL=env$L[1] * pars$astar,
    jCP=max(0, synth(jL * pars$nLC, (H$jCw[1] + H$jCO2p[1] + H$jCO2a[1])*H$H/S, pars$jCPm), na.rm=T),
    jeL=max(jL - jCP/pars$nLC, 0),
    jNPQ=pars$kNPQ/pars$nLC,
    jCO2w=(H$jCw + H$jCO2)*H$H/S - jCP,
    jSG=pars$jSGm/10,
    rhoC=jCP, 
    jNw=0,
    jST=pars$jST0,
    rNS=jST * pars$nNS * pars$sigmaNS,
    rCS=jST * pars$sigmaCS,
    cROS=1,
    dS.Sdt=1)
  S[2:nrow(S), 2:ncol(S)] <- NA

@@

    # Photosynthesis SU
    # =================
    # Light input flux
    S$jL[t] <- (1.256307 + 1.385969 * exp(-6.479055 * (S$S[t-1]/H$H[t-1]))) * env$L[t] * pars$astar
    # CO2 input flux
    H$jCO2p[t] <- pars$jCO2p # passive CO2 flux from the environment
    H$jCO2a[t] <- pars$jCO2a  # active delivery of CO2 from the environment (mediated by the host)
    H$jCO2[t] <- H$jCO2p[t] + H$jCO2a[t]  # Total CO2 input from the environment
    S$rCS[t] <- pars$jST0 * pars$sigmaCS  # metabolic CO2 recycled from symbiont biomass turnover
    H$rCH[t] <- H$jHT[t-1] * pars$sigmaCH  # metabolic CO2 recycled from host biomass turnover
    H$jCw[t-1] <- H$jCw[t-1]  # carbon rejected from host biomass SU, given back as CO2 to photosynthesis
    # Production flux (photosynthetic carbon fixation)
    S$jCP[t] <- synth(S$jL[t] * pars$nLC, (kCO2*H$jCw[t-1] + H$jCO2[t] + H$rCH[t])*H$H[t-1]/S$S[t-1] + S$rCS[t], pars$jCPm) / S$cROS[t-1]

@@

    # Host biomass SU
    # ===============
    # Food input flux (prey=both carbon and nitrogen)
    H$jX[t] <- (pars$jXm * env$X[t] / (env$X[t] + pars$KX))  # Prey uptake from the environment
    # Nitrogen input flux
    H$jN[t] <- (pars$jNm * env$N[t] / (env$N[t] + pars$KN))  # N uptake from the environment
    H$rNH[t] <- H$jHT[t-1] * pars$nNH * pars$sigmaNH  # Recycled N from host biomass turnover
    # Carbon input flux
    S$rhoC[t] <- S$rhoC[t]  # Carbon shared by the symbiont (defined above)
    # Add dissolved organic carbon uptake
    # Production flux (host biomass formation)
    H$jHG[t] <- synth(S$rhoC[t]*S$S[t-1]/H$H[t-1] + H$jX[t], (H$jN[t] + pars$nNX*H$jX[t] + H$rNH[t]) / pars$nNH, pars$jHGm)
    # Rejection flux: nitrogen (surplus nitrogen shared with the symbiont)
    H$rhoN[t] <- max(H$jN[t] + pars$nNX * H$jX[t] + H$rNH[t] - pars$nNH * H$jHG[t], 0)
    # Rejection flux: carbon -- given back to symbiont as CO2 input to photosynthesis
    H$jCw[t] <- max(H$jX[t] + S$rhoC[t]*S$S[t-1]/H$H[t-1] - H$jHG[t], 0)

@@

@@

### Light stress with new model
```{r Lstress_new, cache=T, message=F, warning=F}
# Set up simulation
time <- seq(1,1230,1)
env <- init_env(time=time, L=c(10,40,2), N=c(1e-7,1e-7,2), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, kCO2=2,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0)),
                 NPQ="fixed2")
plot_run_wC(run)
```

@@

# Steady state behavior of new model
```{r new_steadystates_code, message=F, warning=F, include=F}
run_steady_states <- function(time, pars, at, outfile=NULL, runtime=F, food=0) {
  #
  run_coral_wC <- get("run_coral_wC")
  # Load libraries
  require(foreach)
  require(parallel)
  require(doParallel)
  require(reshape2)
  require(dplyr)

@@

  # Run simulations in parallel for each combination of "at" values
  start <- proc.time()  # Start timer...
  # Calculate steady states...
  steady_states <- foreach(i=1:nrow(at), .combine='rbind', .packages='dplyr') %dopar% {
    L <- at[i,]$L; N <- at[i,]$N
    env <- init_env(time=time, L=c(L,L,0), N=c(N,N,0), X=c(food,food,0))
    run <- run_coral_wC(time=time, env=env, pars=pars, NPQ="fixed2")
    ss <- lapply(run[c("H", "S")], function(x) x[length(time), ])
    gr <- ss$H$dH.Hdt
    sh <- ss$S$S/ss$H$H
    hl <- with(ss, log(  pmin(S$rhoC*S$S/H$H + H$jX, pars$jHGm) / pmin((H$jN + pars$nNX*H$jX + H$rNH) / pars$nNH, pars$jHGm)  ))
    sl <- with(ss, log(  pmin(S$jCP, pars$jSGm)   /   pmin((H$rhoN*H$H/S$S + S$rNS)/pars$nNS, pars$jSGm)  ))
    ee <- with(ss, max(0, S$jL - (S$jCP/run$pars$nLC + run$pars$kNPQ)))
    pl <- with(ss, log(   pmin((H$jCw + H$jCO2 + H$rCH)*H$H/S$S + S$rCS, pars$jCPm)   /   pmin(S$jL * pars$nLC, pars$jCPm)    ))
    data.frame(gr=gr, sh=sh, hl=hl, sl=sl, ee=ee, pl=pl)
  }
  stopCluster(cl)  # Stop cluster
  if (runtime==T) print(proc.time() - start)  # Print time elapsed if runtime==T

@@

## Starting biomass = 0.01
```{r run_new_steadystates, cache=T, message=F, warning=F}
# Set time and parameters 
time <- seq(1,200,0.5) 
defpars <- def_pars()
defpars <- replace(defpars, "jHGm", 1)
pars <- replace(defpars, c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                          c(60,       60,    1,   5,      0.9,     0.9,       0,       0,      0.01))
# Set values of L and N at which to get steady state values 
at <- expand.grid(L=seq(from=0, to=60, length.out=21),
                  N=seq(from=0, to=4e-6, length.out=21))

## Starting biomass = 0.1
```{r run_new_steadystates.1, cache=T, message=F, warning=F}
# Set time and parameters 
time <- seq(1,200,0.5) 
defpars <- def_pars()
defpars <- replace(defpars, "jHGm", 1)
pars <- replace(defpars, c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                          c(60,       60,    1,   5,      0.9,     0.9,       0,       0,      0.1))
# Set values of L and N at which to get steady state values 
at <- expand.grid(L=seq(from=0, to=60, length.out=21),
                  N=seq(from=0, to=4e-6, length.out=21))

## Starting biomass = 0.5
```{r run_new_steadystates.5, cache=T, message=F, warning=F}
# Set time and parameters 
time <- seq(1,200,0.5) 
defpars <- def_pars()
defpars <- replace(defpars, "jHGm", 1)
pars <- replace(defpars, c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                          c(60,       60,    1,   5,      0.9,     0.9,       0,       0,      0.5))
# Set values of L and N at which to get steady state values 
at <- expand.grid(L=seq(from=0, to=60, length.out=21),
                  N=seq(from=0, to=4e-6, length.out=21))

```{r testing, cache=T, message=F, warning=F, eval=F, include=F}
# Set up simulation
time <- seq(1,200,0.1) 
env <- init_env(time=time, L=c(2,2,0), N=c(1e-7,3.5e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1)),
                 NPQ="fixed2")
plot_run_wC(run)
# Do elevated nutrients prevent coral from recovering from bleaching? Start with 0.01 initS, constant light (10), lower DIN (1e-7) --> recovery and pos. growth; higher DIN (1e-6) --> no recovery, neg. growth...
```

## Starting symbiont biomass = 1
```{r run_new_steadystates1, cache=T, message=F, warning=F}
# Set time and parameters 
time <- seq(1,200,0.5) 
pars <- replace(defpars, c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                          c(60,       60,    1,   5,      0.9,     0.9,       0,       0,       1))
# Set values of L and N at which to get steady state values 
at <- expand.grid(L=seq(from=0, to=60, length.out=21),
                  N=seq(from=0, to=4e-6, length.out=21))

@@

# Stability at high nitrogen...?
## When system starts at 2 µM DIN and increases to 4 µM DIN, switch is btw. 0.15 and 0.2 initS.
```{r incrN1, cache=T, message=F, warning=F}
# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(1e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 0.15)),
                 NPQ="fixed2")
plot_run_wC(run)

# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(1e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 0.2)),
                 NPQ="fixed2")
plot_run_wC(run)
```

## When system starts at 2 µM DIN and increases to 4 µM DIN, switch is btw. 0.2 and 0.3 initS.
```{r incrN2, cache=T, message=F, warning=F}
# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(2e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, kCO2=5,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1, 0.2)),
                 NPQ="fixed2")
plot_run_wC(run)

# Set up simulation
env <- init_env(time=time, L=c(9,9,0), N=c(2e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, kCO2=5,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1, 0.3)),
                 NPQ="fixed2")
plot_run_wC(run)
```

```{r}
# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(4e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, kCO2=5,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1, 0.5)),
                 NPQ="fixed2")
plot_run_wC(run)

# Set up simulation
env <- init_env(time=time, L=c(10,10,0), N=c(4e-6,4e-6,0), X=c(0,0,0))
# Run new model (sets jCO2a and jCO2p to zero; CO2 is delivered by jCw)
run <- run_coral_wC(time=time, env=env, kCO2=5,
                 pars=replace(defpars, 
                              c("kNPQ", "kROS", "k", "b", "sigmaCS", "sigmaCH", "jCO2a", "jCO2p", "jHGm", "initS"), 
                              c(60,       60,    1,   5,      0.9,         0.9, 0, 0, 1, 0.01)),
                 NPQ="fixed2")
plot_run_wC(run)
with(run, {
  plot(S$S/H$H, S$jSG)
})

```
